### 2021-04-07 LaTeX-ACM/sections/paper.tex
updates

\paragraph{Contributions.} We study fully on-chain markets through design and implementation with Solidity---a high-level programming language for Ethereum that is syntactically similar to Java~\cite{Ethereum41:online}. We choose Ethereum as a hostile environment for an order book: Ethereum is fully decentralized (hardest to regulate), network participation is open to anyone on the internet (strongest adversarial model), and, as a result, it is slow (a lower-bound benchmark). Generally if an application is feasible on Ethereum, it will also be feasible and only run faster on a private (or permissioned) blockchain (\eg Hyperledger), which is a blockchain operated by authorized network nodes only, generally visible to regulators.

@@

\subsubsection*{Acknowledgements.}  The authors thanks the AMF (Autorité des Marchés Financiers) for supporting this research project. J. Clark also acknowledges partial funding from the National Sciences and Engineering Research Council (NSERC)/Raymond Chabot Grant Thornton/Catallaxy Industrial Research Chair in Blockchain Technologies, as well as NSERC through a Discovery Grant. M. Moosavi acknowledges support from Fonds de Recherche du Québec - Nature et Technologies (FRQNT).

%GitHub repo:  \footnote{\CallMarketRepo}

>>>>

\textbf{Contributions.} We study fully on-chain markets through design and implementation with Solidity---a high-level programming language for Ethereum that is syntactically similar to Java~\cite{Ethereum41:online}. We choose Ethereum as a hostile environment for an order book: Ethereum is fully decentralized (hardest to regulate), network participation is open to anyone on the internet (strongest adversarial model), and, as a result, it is slow (a lower-bound benchmark). Generally if an application is feasible on Ethereum, it will also be feasible and only run faster on a private (or permissioned) blockchain (\eg Hyperledger), which is a blockchain operated by authorized network nodes only, generally visible to regulators.

@@

\begin{acks} 
The authors thanks the AMF (Autorité des Marchés Financiers) for supporting this research project. J. Clark also acknowledges partial funding from the National Sciences and Engineering Research Council (NSERC)/Raymond Chabot Grant Thornton/Catallaxy Industrial Research Chair in Blockchain Technologies, as well as NSERC through a Discovery Grant. M. Moosavi acknowledges support from Fonds de Recherche du Québec - Nature et Technologies (FRQNT).
\end{acks}
%GitHub repo:  \footnote{\CallMarketRepo}
